---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_lm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linearRegressionModel)
```

# Introduction

This vignette demonstrates the usage of a custom R package for performing linear regression. The package includes three main functions: my_lm, print.mylm, and my_summary. These functions are designed to mimic the functionality of R's built-in lm function and associated methods.

# Installation

```{r}
#library(devtools)
#devtools::install_github("https://github.com/hJeOlHeNn/biostat-HW3")
#library(linearRegressionModel)
```

# Usage

## Linear Regression with my_lm

The my_lm function performs linear regression. Here's an example using the mtcars dataset:

```{r}
data(mtcars)

fit1 <- my_lm(mpg ~ wt + cyl, data = mtcars)
```

Use * to include interaction variables.

```{r}
fit2 <- my_lm(mpg ~ wt*cyl, data = mtcars)
```

Use -1 to remove intercept from the model.

```{r}
fit3 <- my_lm(mpg ~ -1 + wt + cyl, data = mtcars)
```

## Viewing Results with print.mylm

To view the results of the linear regression, use print.mylm:

```{r}
print.mylm(fit1)
```

## Summary Statistics with my_summary

For a detailed summary of the regression model, use my_summary:

```{r}
my_summary(fit1)
```

# Comparison with R's Built-in Functions

## Correctness

We'll compare the results of my_lm with R's lm function to ensure correctness.

```{r}
# compare my_lm using model 1
fit_builtin1 <- lm(mpg ~ wt + cyl, data = mtcars)
all.equal(as.numeric(fit1$coefficients), as.numeric(fit_builtin1$coefficients))

# compare my_lm using model 2
fit_builtin2 <- lm(mpg ~ wt*cyl, data = mtcars)
all.equal(as.numeric(fit2$coefficients), as.numeric(fit_builtin2$coefficients))

# compare my_lm using model 3
fit_builtin3 <- lm(mpg ~ -1 + wt + cyl, data = mtcars)
all.equal(as.numeric(fit3$coefficients), as.numeric(fit_builtin3$coefficients))

# compare my_summary r square
all.equal(my_summary(fit1)$r_squared, summary(fit_builtin1)$r.squared)

# compare my_summary adjusted r square
all.equal(as.numeric(my_summary(fit1)$adjusted_r_squared), as.numeric(summary(fit_builtin1)$adj.r.squared))
```

## Efficiency

We'll use the bench package to compare the performance of my_lm and lm.

```{r}
# compare efficiency of my_lm
bench::mark(
  as.numeric(fit1$coefficients),
  as.numeric(fit_builtin1$coefficients),
  iterations = 10,
  check = TRUE
)

# compare efficiency of my_summary
bench::mark(
  my_summary(fit1),
  summary(fit_builtin1),
  iterations = 10,
  check = FALSE
)
```

# Conclusion

This vignette has demonstrated how to use the my_lm, print.mylm, and my_summary functions from the My Linear Regression Package and compared them with R's built-in linear regression functions. The package aims to provide an alternative implementation of linear regression analysis in R.
